---
title: "Diversity data collected from NSF fair"
output: html_notebook
---

```{r}
# Loading relevant packages
library(tidyverse)
library(plyr) #used for importing data
```

Importing the dataset and tidying dataset to include only participants who participated in Study 2, answered attention checks correctly, and are the correct age

```{r}
# Getting working directory and specifying we want the data folder in that directory
getwd()
setwd("./data")

# Importing all files in working directory into single datafile
files <- list.files()
data <- adply(files, 1, read.csv)

# Adding participant numbre to dataset
setwd("..")
source("R/nsfAddParticipant.R")
data <- nsf_add_participant(data)

# Filtering out only study 2 participants
data <- subset(data, study == 2)

# Subsetting data where attention check was answered correctly
source("R/attention_check.R")
data <- attention_check(data)

# Removing participants outside of age range
data <- subset(data, age != 99)

# Paring dataset down to only columns relevant for analyses
data <- data[,c("participant","age","condition","trial","response")]

# Separting response column into two columns 
data <- separate(data = data, col = response, into = c("response1", "response2"), sep = "\\;")
```

Getting counts per age group. 

```{r}
count_per_cell <- data %>% 
                    dplyr::count(age, condition)
```

Computing the means for each condition 

```{r}
data_means <- aggregate(as.numeric(response1) ~ age+condition, data, mean)
data_means_temp <- aggregate(as.numeric(response2) ~ age+condition, data, mean)
data_means <- cbind(data_means, data_means_temp)
names(data_means)[names(data_means) == "as.numeric(response1)"] <- "response1"
names(data_means)[names(data_means) == "as.numeric(response2)"] <- "response2"
data_means <- subset(data_means, age < 12)
data_means <- data_means[, c(1:3,6)]

data_numeric <- subset(data, age < 12)
data_numeric$response1 <- as.numeric(data_numeric$response1)
data_numeric$response1 <- as.numeric(data_numeric$response2)
data_numeric$age <- as.integer(data_numeric$age)
```


```{r}

```

Creating graphs for each condition by age
```{r}

plot_diversity <- ggplot(data = data_means) + 
  facet_grid (
    . ~ age
  ) +
  scale_y_continuous(expand = c(0, 0)
  ) +
  coord_cartesian(ylim=c(0.9,5.1)
  ) + 
  labs(x = "Condition",
       y =" Average Response"
  ) +
  theme(text         = element_text(size = 14),
        axis.title.x = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        strip.text = element_text(size = 12),
        strip.background = element_blank(),
        panel.border = element_rect(color = "black", fill = NA),
        panel.background = element_rect(fill = NA)
  ) +
  geom_point(data = data_numeric, 
             aes(y = response1, x = condition),
             position = position_jitter(w = 0.25, h = 0),
             shape = 1,
             size = 2) +
  geom_point(aes(x = condition, y = response1, color = "Response 1"),
             shape = 16,
             size = 7) +
  geom_point(aes(x = condition, y = response2, color = "Response 2"),
             shape = 16,
             size = 7
  ) 
plot_diversity

```


```{r}
data$same <- ifelse(data$response1 == data$response2, 1, 0)
data_no_same <- subset(data, same == 0)

data_no_same_means <- aggregate(as.numeric(response1) ~ age+condition, data_no_same, mean)
data_means_temp <- aggregate(as.numeric(response2) ~ age+condition, data_no_same, mean)
data_no_same_means <- cbind(data_no_same_means, data_means_temp)
names(data_no_same_means)[names(data_no_same_means) == "as.numeric(response1)"] <- "response1"
names(data_no_same_means)[names(data_no_same_means) == "as.numeric(response2)"] <- "response2"
data_no_same_means <- subset(data_no_same_means, age < 12)
data_no_same_means <- data_no_same_means[, c(1:3,6)]

data_no_same_numeric <- subset(data_no_same, age < 12)
data_no_same_numeric$response1 <- as.numeric(data_no_same_numeric$response1)
data_no_same_numeric$response1 <- as.numeric(data_no_same_numeric$response2)
data_no_same_numeric$age <- as.integer(data_no_same_numeric$age)
```


```{r}

plot_diversity1 <- ggplot(data = data_no_same_means) + 
  facet_grid (
    . ~ age
  ) +
  scale_y_continuous(expand = c(0, 0)
  ) +
  coord_cartesian(ylim=c(0.9,5.1)
  ) + 
  labs(x = "Condition",
       y =" Average Response"
  ) +
  theme(text         = element_text(size = 14),
        axis.title.x = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        strip.text = element_text(size = 12),
        strip.background = element_blank(),
        panel.border = element_rect(color = "black", fill = NA),
        panel.background = element_rect(fill = NA)
  ) +
  geom_point(data = data_no_same_numeric, 
             aes(y = response1, x = condition),
             position = position_jitter(w = 0.25, h = 0),
             shape = 1,
             size = 2) +
  geom_point(aes(x = condition, y = response1, color = "Response 1"),
             shape = 16,
             size = 7) +
  geom_point(aes(x = condition, y = response2, color = "Response 2"),
             shape = 16,
             size = 7
  ) 
plot_diversity1
```

Binary data 
```{r}
# Copies dataset
data_binary <- data_numeric

# Adjusting response values to be binary
data_binary$response1[data_binary$response1 == "1"] <- "5"
data_binary$response1[data_binary$response1 == "2" | data_binary$response1 == "4" ] <- "3"
data_binary$response2[data_binary$response2 == "1"] <- "5"
data_binary$response2[data_binary$response2 == "2" | data_binary$response2 == "4" ] <- "3"

# Aggregating new set of means for binary dataset
data_means_binary <- aggregate(as.numeric(response1) ~ age+condition, data_binary, mean)
data_means_temp <- aggregate(as.numeric(response2) ~ age+condition, data_binary, mean)
data_means_binary <- cbind(data_means_binary, data_means_temp)
names(data_means_binary)[names(data_means_binary) == "as.numeric(response1)"] <- "response1"
names(data_means_binary)[names(data_means_binary) == "as.numeric(response2)"] <- "response2"
data_means_binary <- data_means_binary[, c(1:3,6)]
```


```{r}
plot_diversity2 <- ggplot(data = data_means_binary) + 
  facet_grid (
    . ~ age
  ) +
  scale_y_continuous(expand = c(0, 0)
  ) +
  coord_cartesian(ylim=c(0.9,5.1)
  ) + 
  labs(x = "Condition",
       y =" Average Response"
  ) +
  theme(text         = element_text(size = 14),
        axis.title.x = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 14, 
                                    face = "bold",
                                    margin = margin(t = 0, r = 20, b = 0, l = 0)),
        strip.text = element_text(size = 12),
        strip.background = element_blank(),
        panel.border = element_rect(color = "black", fill = NA),
        panel.background = element_rect(fill = NA)
  ) +
  geom_point(data = data_numeric, 
             aes(y = response1, x = condition),
             position = position_jitter(w = 0.25, h = 0),
             shape = 1,
             size = 2) +
  geom_point(aes(x = condition, y = response1, color = "Response 1"),
             shape = 16,
             size = 7) +
  geom_point(aes(x = condition, y = response2, color = "Response 2"),
             shape = 16,
             size = 7
  ) 
plot_diversity2
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
