---
title: "Developmental changes in strategies for gathering evidence about biological kinds: Results"
author: "Emily Foster-Hanson\\*, Kelsey Moty\\*, John Daryl Ocampo, Amanda Cardarelli, and Marjorie Rhodes"
date: "Last updated January 7, 2019"
output:
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

## Loading libraries
library(tidyverse)
library(ordinal) # used for ordinal logistic regressions
library(ucminf) # pretty sure ordinal imports it but will import it explicitly
library(lme4) # ^^^
library(emmeans) # used for ordinal post-hoc pairwise comparisons
library(here) # for loading data
library(Rmisc) # for summarySE
library(knitr)
library(effects)
```

```{r cleaning, include=FALSE}
# Cleaning up the datasets
clean_data <- here::here("cleaning", "diversity_data_cleaning.R")
source(clean_data)
```

```{r import_data, include=FALSE}
# Read in the data file
dt2 <- here::here("data", "diversity_fulldataset_cleaned.csv") %>% 
  read_csv() 

# Converting variables to integers 
dt2$exp_choice <- factor(dt2$exp_choice)
dt2$response <- factor(dt2$response)
dt2$age_factor <- factor(dt2$age_factor)
```

```{r import_demo, include=FALSE}
# Cleaning up demographics
get_demographics <- here::here("cleaning","diversity_cleaning_demographics.R")
source(get_demographics)
```

*2.1 Participants*

Participants included children ages 5-6 (*N* = `r nrow(diversity_demo5.6)`; *M* age = `r round(mean(diversity_demo5.6$age_exact, na.rm = TRUE), 2)`; `r sum(diversity_demo5.6$Gender == "Male")` male), 7-8 (*N* = `r nrow(diversity_demo7.8)`; *M* age = `r round(mean(diversity_demo7.8$age_exact, na.rm = TRUE), 2)`; `r sum(diversity_demo7.8$Gender == "Male")` male), and 9-10 (*N* = `r nrow(diversity_demo9.10)`; *M* age = `r round(mean(diversity_demo9.10$age_exact, na.rm = TRUE), 2)`; `r sum(diversity_demo9.10$Gender == "Male")` male), recruited and tested in the American Museum of Natural History (AMNH) in New York City; most were from urban and suburban environments across the United States. 
Children whose parents provided demographics information (`r round((sum(diversity_demo_child_keepers$RE == "Unreported", na.rm = TRUE))/nrow(diversity_demo_child_keepers)*100, 0)`% chose not to) were `r round((sum(diversity_demo_child_keepers_reported$RE == "White", na.rm = TRUE))/nrow(diversity_demo_child_keepers_reported)*100, 0)`% White, `r round((sum(diversity_demo_child_keepers_reported$RE == "Black", na.rm = TRUE))/nrow(diversity_demo_child_keepers_reported)*100, 0)`% Black, `r round((sum(diversity_demo_child_keepers_reported$RE == "Asian", na.rm = TRUE))/nrow(diversity_demo_child_keepers_reported)*100, 0)`% Asian, and `r round((sum(diversity_demo_child_keepers_reported$RE == "Mixed", na.rm = TRUE))/nrow(diversity_demo_child_keepers_reported)*100, 0)`% more than one race; of these, `r round((sum(diversity_demo_child_keepers_reported$Hispanic == "1", na.rm = TRUE))/nrow(diversity_demo_child_keepers_reported)*100, 0)`% were Hispanic (of any race). For additional background information about the sample (including parental report of their children's experiences with nature), see https://osf.io/6yts8/. Parents provided written informed consent and children gave verbal assent. The Institutional Review Boards of the authors' university and of AMNH approved all study procedures. The data of 6 additional children were not recorded because they chose not to complete the study; an additional 22 children began testing but are not included in analyses because of technical issues during testing.

Participants also included adults (*N* = `r nrow(diversity_demo_adult)`; *M* age = `r round(mean(diversity_demo_adult$age_exact, na.rm = TRUE), 2)`; `r sum(diversity_demo_adult$Gender == "Male")` male; `r round((sum(diversity_demo_adult$RE == "White", na.rm = TRUE))/nrow(diversity_demo_adult)*100, 0)`% White, `r round((sum(diversity_demo_adult$RE == "Black or African American", na.rm = TRUE))/nrow(diversity_demo_adult)*100, 0)`% Black, `r round((sum(diversity_demo_adult$RE == "Asian", na.rm = TRUE))/nrow(diversity_demo_adult)*100, 0)`% Asian, `r round((sum(diversity_demo_adult$RE == "Mixed", na.rm = TRUE))/nrow(diversity_demo_adult)*100, 0)`% more than one race, and `r round((sum(diversity_demo_adult$RE == "Unreported", na.rm = TRUE))/nrow(diversity_demo_adult)*100, 0)`% unreported; `r round((sum(diversity_demo_adult$hispanic == "1", na.rm = TRUE))/nrow(diversity_demo_adult)*100, 0)`% were Hispanic/Latino of any race) recruited from Amazon Mechanical Turk. Three additional adults were excluded because they failed to correctly answer attention checks.

```{r set_condition, include=FALSE}
# Analyses on diversity condition
# Ordinal logistic regression with both adult and child data (age treated as categorical)
olr_diversity <- here::here("analyses","olr_diversity.R")
source(olr_diversity)

# Ordinal logistic regression with just children's data, with age as a continuous variable
olr_diversity_child <- here::here("analyses","olr_diversity_child.R")
source(olr_diversity_child)

# Ordinal logistic regression for children's data broken down by experimenter choice
olr_diversity_child_by_exp_choice <- here::here("analyses","olr_diversity_child_by_exp_choice.R")
source(olr_diversity_child_by_exp_choice)

# Summary of participants' responses in the Set Condition
set_summary <- here::here("analyses", "diversity_summary.R")
source(set_summary)
```

```{r single_condition, include=FALSE}
# Analyses on Single condition
# Ordinal logistic regression on control condition data (both adults and kids)
olr_control <- here::here("analyses","olr_control.R")
source(olr_control)

# Ordinal logistic regression on control condition data (just kid data)
olr_control_child <- here::here("analyses","olr_control_child.R")
source(olr_control_child)

# Summary of participants' responses in the Single Condition
single_summary <- here::here("analyses", "control_summary.R")
source(single_summary)
```

```{r both_conditions, include=FALSE }
# Analyses on full dataset
## Ordinal logistic regression on full dataset comparing condition by age 
olr_full <- here::here("analyses","olr_full.R")
source(olr_full)

## Ordinal logistic regression on full dataset comparing condition by age (child data only)
olr_full_child <- here::here("analyses","olr_full_child.R")
source(olr_full_child)
```


**2. Results**

**2.1 Set condition**

**2.1.1 Experimental data analyses.** We analyzed participants' choices on the animal scales using an ordinal logistic regression. For analyses including adults, we treated age as a categorical variable; for comparable analyses with children only, we treated age as a continuous variable. We report the results of likelihood ratio tests and means with 95% confidence intervals

In the Set condition, adult and child participants' samples varied by age ($\chi^2$(`r diversity_main$Df[3]`) = `r round((diversity_main$LRT[3]),2)`, *p* < `r ifelse(diversity_main[3,4] < .001, .001, round(diversity_main[3,4],3))`) and character choice ($\chi^2$(`r diversity_main$Df[2]`) = `r round((diversity_main$LRT[2]),2)`, *p* < `r ifelse(diversity_main[2,4] < .001, .001, round(diversity_main[2,4],3))`) with a marginal interaction between age and character choice ($\chi^2$(`r diversity_int$Df[2]`) = `r round((diversity_int$LRT[2]),2)`, *p* = `r ifelse(diversity_int[2,4] < .001, .001, round(diversity_int[2,4],2))`). When the character chose the *least* extreme exemplar as the first element in the sample (exemplar 1, e.g., the slowest cheetah), all participants selected maximally extreme and, therefore, maximally diverse exemplars as the second element in the sample (Ages 5-6: *M* = `r round(data_summary$response[1],2)`, 95% CI [`r round(data_summary$response[1]-data_summary$ci[1],2)`, `r round(data_summary$response[1]+data_summary$ci[1],2)`]; Ages 7-8: *M* = `r round(data_summary$response[6],2)`, 95% CI [`r round(data_summary$response[6]-data_summary$ci[6],2)`, `r round(data_summary$response[6]+data_summary$ci[6],2)`]; Ages 9-10: *M* = `r round(data_summary$response[11],2)`, 95% CI [`r round(data_summary$response[11]-data_summary$ci[11],2)`, `r round(data_summary$response[11]+data_summary$ci[11],2)`]; Adults: *M* = `r round(data_summary$response[16],2)`, 95% CI [`r round(data_summary$response[16]-data_summary$ci[16],2)`, `r round(data_summary$response[16]+data_summary$ci[16],2)`]; Figure 2). However, when the character selected the *most* extreme exemplar as the first element in the sample (exemplar 5, e.g., the fastest cheetah), younger children selected more extreme (i.e., exemplar 4)-and, therefore, less diverse-exemplars as the second element in the sample (Ages 5-6: *M* = `r round(data_summary$response[5],2)`, 95% CI [`r round(data_summary$response[5]-data_summary$ci[5],2)`, `r round(data_summary$response[5]+data_summary$ci[5],2)`]; Ages 7-8: *M* = `r round(data_summary$response[10],2)`, 95% CI [`r round(data_summary$response[10]-data_summary$ci[10],2)`, `r round(data_summary$response[10]+data_summary$ci[10],2)`]) while older children (Ages 9-10: *M* = `r round(data_summary$response[15],2)`, 95% CI [`r round(data_summary$response[15]-data_summary$ci[15],2)`, `r round(data_summary$response[15]+data_summary$ci[15],2)`]) and adults (*M* = `r round(data_summary$response[20],2)`, 95% CI [`r round(data_summary$response[20]-data_summary$ci[20],2)`, `r round(data_summary$response[20]+data_summary$ci[20],2)`]) chose less extreme, more diverse, exemplars. Younger children's preferred samples were, thus, both less diverse and more extreme than those preferred by older children and adults. Age-related changes in sample selection strategies held even when only examining data from children, with children's exact age included in the model as a continuous variable (Fig. 2). These results are consistent with our first pre-registered hypothesis.


```{r plot, echo=FALSE}
plotting_continuous_diversity <- here::here("plots", "plot_continuous_diversity.R")
source(plotting_continuous_diversity)

plot_continuous_diversity
```
*Figure 2*

Participant selections on the animal scales in the Test condition, by character choice, on the animal scale. Lines represent children's average responses across age, and green shaded area reflects 95% confidence intervals. Large triangles reflect adults' group average responses, and error bars reflect 95% confidence intervals. Small dots reflect individual participant responses. Age is treated continuously on the x-axis, except for adults (who are graphed as a single group). Higher values are more extreme on characteristic features. Pairwise comparisons revealed that 7-8 year olds chose significantly less diverse samples than 9-10 year olds (*t* = `r round(diversity_pairwise$contrasts$estimate[4],2)`, *SE* = `r round(diversity_pairwise$contrasts$SE[4],2)`, *p* = `r round(diversity_pairwise$contrasts$p.value[4],2)`) but did not differ significantly from 5-6 year olds (*t* = `r round(diversity_pairwise$contrasts$estimate[1],2)`, *SE* = `r round(diversity_pairwise$contrasts$SE[1],2)`, *p* = `r round(diversity_pairwise$contrasts$p.value[1],2)`); 9-10 year olds' responses did not differ significantly from adults' (*t* = `r round(diversity_pairwise$contrasts$estimate[6],2)`, *SE* = `r round(diversity_pairwise$contrasts$SE[6],2)`, *p* = `r round(diversity_pairwise$contrasts$p.value[6],2)`).

**2.2. Single condition**
Next, we examined participants' choices on the animal scales in the Single condition relative to the Set condition. Akin to the experimental analyses from the Set condition, we analyzed these data using ordinal logistic regression, with one model including adults (age treated as categorical) and one with child data only (age treated as continuous). We report the results of likelihood ratio tests and means with 95% confidence intervals. 

Consistent with our registered hypothesis, we found a significant interaction between age and condition when examining the child data alone ($\chi^2$(`r ordinal_full_int_child$Df[2]`) = `r round(ordinal_full_int_child$LRT[2],2)`, *p* = `r round(ordinal_full_int_child[2,4],2)`); the interaction was marginal but not significant when the adult data was included ($\chi^2$(`r ordinal_full_int$Df[2]`) = `r round(ordinal_full_int$LRT[2],2)`, *p* = `r round(ordinal_full_int[2,4],2)`). This supports our predictions that younger children's choices would vary less in terms of condition, and that they would pick similarly ideal exemplars regardless of whether they were choosing a single exemplar on their own (Single condition: younger children ages 5-8: *M* = `r round(data_summary_single$response[1], 2)`, *SD* = `r round(data_summary_single$sd[1], 2)`; older children ages 9-10: *M* = `r round(data_summary_single$response[2], 2)`, *SD* = `r round(data_summary_single$sd[2], 2)`; adults: *M* = `r round(data_summary_single$response[3], 2)`, *SD* = `r round(data_summary_single$sd[3], 2)`) or choosing a second exemplar to create a two-exemplar sample set along with the experimenter's selection (Set condition: younger children ages 5-8: *M* = `r round(data_summary_set$response[1], 2)`, *SD* = `r round(data_summary_set$sd[1], 2)`; older children ages 9-10: `r round(data_summary_set$response[2], 2)`, *SD* = `r round(data_summary_set$sd[2], 2)`; adults: `r round(data_summary_set$response[3], 2)`, *SD* = `r round(data_summary_set$sd[3], 2)`). When breaking down this interaction, we found that age predicted children's choice in the Set condition ($\chi^2$(`r set_child$Df[2]`) = `r round(set_child$LRT[2],2)`, *p* < `r ifelse(set_child[2,4] < .001, ".001", round(set_child[2,4],2))`, simple slope = `r round(ordinal_full_child_emtrends$age_exact.trend[2], 2)`, 95% CI [`r round(ordinal_full_child_emtrends$asymp.LCL[2], 2)`, `r round(ordinal_full_child_emtrends$asymp.UCL[2], 2)`]), with younger children choosing more extreme examples than older children, consistent with the analyses reported earlier. Inconsistent with our pre-registered hypothesis, however, participants' selections did not become less extreme with age in the Single condition ($\chi^2$(`r single_child$Df[2]`) = `r round(single_child$LRT[2],2)`, *p* = `r round(single_child[2,4],2)`, simple slope = `r round(ordinal_full_child_emtrends$age_exact.trend[1], 2)`, 95% CI [`r round(ordinal_full_child_emtrends$asymp.LCL[1], 2)`, `r round(ordinal_full_child_emtrends$asymp.UCL[1], 2)`]), not even when adults were included in the model ($\chi^2$(`r control_main$Df[2]`) = `r round(control_main$LRT[2],2)`, *p* = `r round(control_main[2,4],2)`). Thus, whereas participants in this study began to value more diverse samples with age (as shown in the Set condition), they did not show a shift from more extreme to more average features when asked to learn from a single exemplar (instead, participants selected relatively extreme exemplars across age, consistent with Foster-Hanson & Rhodes, 2019, Study 3). 







