---
title: "Cleaning up data files for diversity analyses"
output: # html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First we need to load in the appropriate libraries and making sure we are in the correct working directory. Currently this file and the data are stored in the same folder, so working directory should be good. 

```{r packageload,error=TRUE, message=FALSE}
# loading libraries needed to tidy data
library(data.table)
library(tidyverse)
library(lubridate)
library(here)
```

Next, we need to read in the correct data file (both the child and adult data files) and merge them together. Currently, the files are merged testable files that need to be cleaned and saved in long format. 

```{r data, error=TRUE, message=FALSE}
#Read in the data files 
#This file contains data from children and adults, in wide format

adult_data <- here::here("data", "diversity_adult_data.csv") %>% read_csv()
child_data <- here::here("data", "diversity_child_data_120718.csv") %>% read_csv()

```

First, to clean up the adult data. 

```{r}
# creating a temporary store of the data to work with and pulling out the relevant columns
temp_data <- adult_data
temp_data <- subset(temp_data, select = c(id, type, head, stim1, response))
temp_data$age <- "adult" # useful column for later data cleaning

# checking if participants answered check questions correctly (the 3 audio checks, lunch/laundry, and the warmups)
# laundry1 answer = 1 laundry2 answer = 3 lunch2 answer = not 2 lunch1 answer = not 3
# AudioCheck = 4 AudioCheck2 = 1 AudioCheck3 = 5 warmup = 2 warmup2 = 2

# assigning a value of 1 to new column "correct" if participants answered in accordance with key above
check <- temp_data %>%
  filter(stim1 %in% c(
    "AudioCheck", "AudioCheck2", "AudioCheck3", "warmup",
    "warmup2", "lunch1", "lunch2", "laundry1", "laundry2"
  )) %>%
  mutate(correct = ifelse(stim1 %in% c("laundry1", "AudioCheck2") & response == "1", 1,
    ifelse(stim1 %in% c("warmup", "warmup2") & response == "2", 1,
      ifelse(stim1 == "laundry2" & response == "3", 1,
        ifelse(stim1 == "AudioCheck" & response == 4, 1,
          ifelse(stim1 == "AudioCheck3" & response == "5", 1,
            ifelse(stim1 == "lunch2" & response != "2", 1,
              ifelse(stim1 == "lunch1" & response != "3", 1, 0)
            )
          )
        )
      )
    )
  )
)

# filtering out participants who answered incorrectly on Audiochecks
check <- subset(
  check,
  correct == "0" &
    (stim1 == "AudioCheck2" |
      stim1 == "AudioCheck3" |
      stim1 == "AudioCheck")
)

# removing participants who missed at least one attention check
temp_data <- anti_join(temp_data, check, by = "id") 

```

Cleaning up the child data

```{r}
temp_data_c <- child_data
temp_data_c <- subset(temp_data_c, select = c(id, type, head, stim1, response))
temp_data_c$age <- "child" # useful column for later data cleaning

# checking if participants answered check questions correctly (lunch/laundry, and the warmups)
# download-4 (that's the audio check) = 2
# laundry11 answer = 1
# laundry21final answer = 3
# lunch2 answer = not 2
# lunch1 answer = not 3
# warmup = 2
# warmup2 = 2

# assigning a value of 1 to new column "correct" if participants answered in accordance with key above
check <- temp_data_c %>% 
  filter(stim1 %in% c("download-4", "warmup", "warmup2", "lunch1", "lunch2", "laundry11", "laundry21final")) %>% 
  mutate(correct = ifelse(stim1 %in% c("laundry11") & response == "1", 1, 
                          ifelse(stim1 %in% c("warmup", "warmup2", "download-4") & response == "2", 1,
                                 ifelse(stim1 == "laundry21final" & response == "3", 1,
                                        ifelse(stim1 == "lunch2" & response != "2", 1,
                                               ifelse(stim1 == "lunch1" & response != "3", 1, 0)
                                               )
                                        )
                                 )
                          )
  )

# WE ARE NOT EXCLUDING CHILDREN FOR WARM UP
# filtering out participants who answered incorrectly on lunch2 or laundry2
# check <- subset(
#   check,
#   correct == "0" &
#     (stim1 == "laundry2" |
#      stim1 == "lunch2")
# )

# removing participants who missed at least one attention check
# temp_data_c <- anti_join(temp_data_c, check, by = "id") 

```

Breaking data into demo datafile and test datafile

```{r}
# binding these two temp datasets together
data <- rbind(temp_data, temp_data_c)

# creating data file for demographic data only
data_demographics <- data %>% filter(type == "form") %>% dplyr::select(id, head, response, age)

# keeping only test trials in main dataset since we no longer need attention check trials
data %<>% filter(type == "test" & !stim1 %in% c("AudioCheck", "AudioCheck2", "AudioCheck3", "warmup", "warmup2", "lunch1", "lunch2", "laundry1", "laundry2", "download-4", "laundry11", "laundry21final")) %>% dplyr::select(id, stim1, response, age)


```

Renaming variables in test file

```{r}
# Creating column to specificy condition
data$condition <- ifelse(endsWith(data$stim1, "introno"), "control", "diversity")

# Creating column to specify item kind -- 
data$item <- ifelse(startsWith(data$stim1, "ch"), "cheetah",
                    ifelse(startsWith(data$stim1, "gi") | startsWith(data$stim1, "gf"), "giraffe",
                           ifelse(startsWith(data$stim1, "sk"), "skunk", 
                                  ifelse(startsWith(data$stim1, "sh"), "shark",
                                         ifelse(startsWith(data$stim1, "po"), "porcupine", "NA")
                                  )
                           )
                    )
)

# Creating column to specify exp_choice, 0 for control condiion
data$exp_choice <- ifelse(data$condition == "control", 0,
                          ifelse(grepl("1", data$stim1), 1,
                                 ifelse(grepl("2", data$stim1), 2,
                                        ifelse(grepl("3", data$stim1), 3,
                                               ifelse(grepl("4", data$stim1), 4,
                                                      ifelse(grepl("5", data$stim1), 5, "NA")
                                               )
                                        )
                                 )
                          )
)

data <- data[,!names(data) %in% c("stim1")]

```

Editing demographics forms 

```{r}
##creating separate demo for child vs adult data and converting to long
child_demographics <- data_demographics %>% 
  filter(age == "child") %>% 
  tidyr::spread(head, response)
adult_demographics <- data_demographics %>% 
  filter(age == "adult") %>% 
  mutate(head = ifelse(!is.na(head), head, 
                       ifelse(as.numeric(response) < 35 | is.na(response), "day", "year"))) %>% 
  spread(head, response)

## EDITING ADULT DEMO
# Getting adults birthdays into single column
# Converting month name to number
i <- 0
for (i in 1:nrow(adult_demographics)){
  adult_demographics[i,3] <- match(adult_demographics[i,3], month.name, nomatch = NA)
  i <- i + 1
}
colnames(adult_demographics)[3] <- "month"

adult_demographics$DOB <- as.character(as.Date.character(with(adult_demographics, paste(month, day, year, sep = "/")), "%m/%d/%Y"))

# Adding DOT column
adult_demographics$DOT <- "2017-10-26"

# removing old columns
adult_demographics <- adult_demographics[,!names(adult_demographics) %in% c("month", "day", "year")]

# computing child's age
adult_demographics$age_exact <- interval(start = adult_demographics$DOB, end = adult_demographics$DOT)/
                                    duration(n = 1, unit = "years")
adult_demographics$age_factor <- "adult"


## EDITING CHILD DEMO
#rename DOB and DOT columns so easier to call
setnames(child_demographics, old = c('Date of Birth:','Test Date:'), new = c('DOB','DOT'))

# formatting date columns
child_demographics$DOB <- parse_date_time(child_demographics$DOB,
                                          orders = c("m/d/y", "m/d/Y"))
child_demographics$DOT <- parse_date_time(child_demographics$DOT,
                                          orders = c("m/d/y", "m/d/Y"))
# computing child's age
child_demographics$age_exact <- interval(start = child_demographics$DOB, end = child_demographics$DOT)/
                                    duration(n = 1, unit = "years")

#Create a new column called "ageGroup" with 3 different age groups 5-6, 7-8, 9-10 in div_dataForm_wide

child_demographics <- child_demographics %>% mutate(age_factor = case_when(age_exact < 7 ~ "5s/6s", 
                                                                                age_exact > 6.999 & age_exact < 9 ~ "7s/8s", 
                                                                                age_exact > 8.99 ~ "9s/10s"))

```

Mergining ages from demo back into main data file

```{r}

# pulling out ages from both demos
a <- c("id", "age_exact", "age_factor")
ages <- rbind(adult_demographics[,names(adult_demographics) %in% a], child_demographics[,names(child_demographics) %in% a])

# merging ages back to main dataset
data <- full_join(data, ages, by = "id")

```

Formatting and exporting data file

```{r}

# order of columns for export
a <- c("id", "condition", "item", "exp_choice", "response", "age_exact", "age_factor")
data <- data[,names(data) %in% a]
data$age_factor <- as.factor(data$age_factor)

write.csv(data, file = "diversity_fulldataset_cleaned.csv", row.names = FALSE)
write.csv(child_demographics, file = "testable_demographics_child.csv", row.names = FALSE)
write.csv(adult_demographics, file = "testable_demographics_adult.csv", row.names = FALSE)

# TODO write_csv is better and faster, but some reason, pushing an error... 
# write_csv(final_data, file.path(dir, "diversity_fulldataset_cleaned.csv"))
```

